\documentclass{resume}

\name{Frank Poon}
\phone{+1 626.757.7872}
\email{frankgpoon@gmail.com}
\website{frankpoon.com}
\linkedin{frankgpoon}
\github{frankgpoon}

\begin{document}
\maketitle

\section{Education}

\school
{University of Washington}
{B.S. Computer Science}
{September 2016 - June 2020}
{Seattle, Washington, USA}
{\textbf{Cumulative GPA:} 3.61 \blt \textbf{Awards:} Dean's List (7 quarters)

  \textbf{Relevant Coursework:} Software Design, Data Structures/Algorithms, 
  Linear Algebra, Differential Equations, Discrete Math, Systems Programming,
  Probability/Statistics, Machine Learning, Computer Architecture

  \textbf{Organizations:} Pi Kappa Alpha Fraternity, Association for Computing
  Machinery
}

\section{Experience}

% \job
% {Amazon Web Services, Inc.}
% {Software Development Engineer Intern}
% {Summer 2019}
% {Seattle, Washington, USA}{aws.amazon.com}
% {
%   Incoming intern.
% }

\job
{University of Washington}
{CSE 331 Teaching Assistant}
{April 2019 - June 2019}
{Seattle, Washington, USA}
{courses.cs.washington.edu/courses/cse331/19sp/}
{
  CSE 331: Software Design and Implementation was taught by Professor Hal 
  Perkins in spring 2019, with enrollment of around 230 students.
  \begin{overview}
    \item Lead discussion sections of 20+ students and teach fundamentals on
          program design, testing, and specification, along with event-driven
          programming and some code reasoning.
    \item Provide tutoring and assistance to students by hosting office hours
          and by answering student questions on the course discussion board.
    \item Attend staff meetings and coordinate with instructor and other staff 
          in preparing material for lectures, sections, assignments, and exams.
    \item Grade student assignments and exams, and provide feedback on student 
          performance overall.
  \end{overview}
}

\job
{Choco Communications GmbH}
{Growth Engineering Intern}
{July 2018 - September 2018}
{Berlin, Germany}
{choco.app}
{
  Choco is a startup with a peer to peer platform for restaurants ordering 
  products from food suppliers.
  \begin{overview}
    \item Implemented modules using node.js that automate conversion between 
          different formats, such as localized PDF invoices and SMS 
          notifications for clients, and Slack/analytics for internal usage.
    \item Improved localization within React Native mobile app and web platform
          by working with clients and developers in multiple EU countries
    \item Built an extensible framework for an automated chatbot using node.js 
          and the XMPP protocol to help with customer support and onboarding.
  \end{overview}
}

\section{Projects}

\project
{Flashcard Study Buddy (Voice-Controlled App for Google Assistant)}
{June 2017 - August 2017}
{frankpoon.com/fsb}
{
  Flashcard Study Buddy is a voice-controlled app for Google Assistant that 
  allows users to search for flash cards and test themselves verbally on them 
  using the Quizlet REST API. It is approved by Google and available on all 
  devices with Google Assistant.
  \begin{overview}
    \item Takes in user input with Google's natural language processing engine 
          DialogFlow.
    \item Processes inputs using a webhook written in node.js and hosted on 
          Firebase.
    \item Implements OAuth 2.0 authentication protocol for users to connect 
          seamlessly to their Quizlet accounts.
  \end{overview}
}

\section{Skills}
\textbf{Programming Languages:} Java, JavaScript, C/C++, Python, bash, HTML, CSS

\textbf{Tools:} git, AWS, Google Cloud, DialogFlow, Firebase, Agile Development,
                Pytorch

\textbf{Technologies:} REST/SOAP, node.js, React, OAuth

\end{document}